### 2024-01-29 ms.qmd
Updates

Originally, we started with 96 lizards, 48 per species and 12 per treatment per species. However, due to natural mortality (n = 11), no completion of the training stage (n = 1), or no motivation during the learning tasks (n = 3), we ended up with a total of 81 lizards. Final sample sizes per treatment and species are disclosed on @tbl-data.  
```{r, models}
#| label: models
# Fitting the model and extraction of posteriors for both species using fit_m function (see func.r in R folder). The result everytime the function is used is a df with the posteriors of the model. The functions saves the model automatically in output/models; and when the parameter refit = FALSE then the posteriors are extracted from the model previously written instead of fitting the model again each time.
source(here("R", "func.R"))
# Model formula: FC_associative ~ Trial*cort*temp + (1 + Trial|lizard_id)
## A.1) L. delicata
deli_red <- fit_m("deli", "red", refit = FALSE)
bayes_R2(deli_red)

write.csv(deli_red, file= "./output/Checking/deli_red.csv")
deli_blue <- fit_m("deli", "blue", refit = FALSE)
write.csv(deli_blue, file= "./output/Checking/deli_blue.csv")
## A.2) L. guichenoti
guich_red <- fit_m("guich", "red", refit = FALSE)
write.csv(guich_red, file= "./output/Checking/guich_red.csv")
guich_blue <- fit_m("guich", "blue", refit = FALSE)
write.csv(guich_blue, file= "./output/Checking/guich_blue.csv")
```

@@

```{r, figdeli}
#| label: figdeli
#| fig.cap: "Deli"
# First step, create the Intercepts for all models
## 1) Associative task
### Group = red
int_dar_CORTCold <- deli_red$b_Intercept
int_dar_ControlCold <- (deli_red$b_cortControl + deli_red$b_Intercept)
int_dar_CORTHot <- (deli_red$b_tempHot + deli_red$b_Intercept)
int_dar_ControlHot <- (deli_red$'b_cortControl:tempHot' + deli_red$b_cortControl + deli_red$b_tempHot + deli_red$b_Intercept)
### Group = blue
int_dab_CORTCold <- deli_blue$b_Intercept
int_dab_ControlCold <- (deli_blue$b_cortControl + deli_blue$b_Intercept)
int_dab_CORTHot <- (deli_blue$b_tempHot + deli_blue$b_Intercept)
int_dab_ControlHot <- (deli_blue$'b_cortControl:tempHot' + deli_blue$b_cortControl + deli_blue$b_tempHot + deli_blue$b_Intercept)

@@

```{r, figguich}
#| label: Figguich
#| fig.cap: "Guich"
```

@@

#### Colour preference
To test if lizards were biased towards the assigned colour as our preliminary analyses suggested, we employed the intercepts  from our posterior distributions. We first estimated the predicted probability of choosing the correct feeder first in the first trial, by using the formula: 
$$\text{Probability} = \frac{1}{1 + e^{-Intercept}}$$

@@

probright_drControlCold <- 1/(1+exp(-(deli_red$b_cortControl + deli_red$b_Intercept)))
probright_drCORTHot <- 1/(1+exp(-(deli_red$b_tempHot + deli_red$b_Intercept)))
probright_drControlHot <- 1/(1+exp(-(deli_red$'b_cortControl:tempHot' + deli_red$b_cortControl + deli_red$b_tempHot + deli_red$b_Intercept)))

@@

probright_dbCORTCold <- 1/(1+exp(-(deli_blue$b_Intercept)))
probright_dbControlCold <- 1/(1+exp(-(deli_blue$b_cortControl + deli_blue$b_Intercept)))
probright_dbCORTHot <- 1/(1+exp(-(deli_blue$b_tempHot + deli_blue$b_Intercept)))
probright_dbControlHot <- 1/(1+exp(-(deli_blue$'b_cortControl:tempHot' + deli_blue$b_cortControl + deli_blue$b_tempHot + deli_blue$b_Intercept)))

@@

probright_grCORTCold <- 1/(1+exp(-guich_red$b_Intercept))
probright_grControlCold <- 1/(1+exp(-(guich_red$b_cortControl + guich_red$b_Intercept)))
probright_grCORTHot <- 1/(1+exp(-(guich_red$b_tempHot + guich_red$b_Intercept)))
probright_grControlHot <- 1/(1+exp(-(guich_red$'b_cortControl:tempHot' + guich_red$b_cortControl + guich_red$b_tempHot + guich_red$b_Intercept)))

@@

probright_gbCORTCold <- 1/(1+exp(-guich_blue$b_Intercept))
probright_gbControlCold <- 1/(1+exp(-(guich_blue$b_cortControl + guich_blue$b_Intercept)))
probright_gbCORTHot <- 1/(1+exp(-(guich_blue$b_tempHot + guich_blue$b_Intercept)))
probright_gbControlHot <- 1/(1+exp(-(guich_blue$'b_cortControl:tempHot' + guich_blue$b_cortControl + guich_blue$b_tempHot + guich_blue$b_Intercept)))

@@

Model formula for task is:  
Choice  ~ Trial*cort*temp + (1 + Trial|lizard_id)  
Plots for the different models of the associative task:  
1.- _L. delicata_  
  1.a.- Red  
```{r , plotmod_dar, out.width="70%", fig.align="center"}
plot(mod_dar)
```
```{r, results='asis', echo=FALSE}
cat("\\newpage")
```

>>>>

Originally, we started with 96 lizards, 48 per species and 12 per treatment per species. However, due to natural mortality (n = 11), no completion of the training stage (n = 1), or no motivation during the learning tasks (n = 3), we ended up with a total of 81 lizards. Final sample sizes per treatment and species are disclosed on @tbl-data.  
```{r, models}
#| label: models
# Fitting the model and extraction of posteriors for both species using fit_m function (see func.r in R folder). The result everytime the function is used is a df with the posteriors of the model. The functions saves the model automatically in output/models; and when the parameter refit = FALSE then the posteriors are extracted from the model previously written instead of fitting the model again each time.
source(here("R", "func.R"))
# Model formula: FC_associative ~ Trial*cort*temp + (1 + Trial|lizard_id)
## A.1) L. delicata
deli_red <- fit_m("deli", "red", refit = FALSE)
write.csv(deli_red, file= "./output/Checking/deli_red.csv")
deli_blue <- fit_m("deli", "blue", refit = FALSE)
write.csv(deli_blue, file= "./output/Checking/deli_blue.csv")
## A.2) L. guichenoti
guich_red <- fit_m("guich", "red", refit = FALSE)
write.csv(guich_red, file= "./output/Checking/guich_red.csv")
guich_blue <- fit_m("guich", "blue", refit = FALSE)
write.csv(guich_blue, file= "./output/Checking/guich_blue.csv")
```

@@

```{r, fig-results}
#| label: figdeli
#| fig.cap: "Deli"
# First step, create the Intercepts for all models
## 1) Associative task
### Group = red
int_dar_CORTCold <- deli_red$b_Intercept
int_dar_ControlCold <- (deli_red$b_cortControl + deli_red$b_Intercept)
int_dar_CORTHot <- (deli_red$b_tempHot + deli_red$b_Intercept)
int_dar_ControlHot <- (deli_red$'b_cortControl:tempHot' + deli_red$b_cortControl + deli_red$b_tempHot + deli_red$b_Intercept)
### Group = blue
int_dab_CORTCold <- deli_blue$b_Intercept
int_dab_ControlCold <- (deli_blue$b_cortControl + deli_blue$b_Intercept)
int_dab_CORTHot <- (deli_blue$b_tempHot + deli_blue$b_Intercept)
int_dab_ControlHot <- (deli_blue$'b_cortControl:tempHot' + deli_blue$b_cortControl + deli_blue$b_tempHot + deli_blue$b_Intercept)

@@

@@

#### Colour preference
To test if lizards were biased towards the assigned colour as our preliminary analyses suggested, we employed the intercepts  from our posterior distributions. We first estimated the predicted probability of choosing the correct feeder first in the first trial, by using the formula: 
$$\text{Probability} = \frac{e^{Intercept}}{1 + e^{Intercept}}$$

@@

probright_drControlCold <- exp(deli_red$b_cortControl + deli_red$b_Intercept)/(1+exp(deli_red$b_cortControl + deli_red$b_Intercept))
probright_drCORTHot <- exp(deli_red$b_tempHot + deli_red$b_Intercept)/(1+exp(deli_red$b_tempHot + deli_red$b_Intercept))
probright_drControlHot <- exp(deli_red$'b_cortControl:tempHot' + deli_red$b_cortControl + deli_red$b_tempHot + deli_red$b_Intercept)/(1+exp(deli_red$'b_cortControl:tempHot' + deli_red$b_cortControl + deli_red$b_tempHot + deli_red$b_Intercept))

@@

probright_dbCORTCold <- exp(deli_blue$b_Intercept)/(1+exp(deli_blue$b_Intercept))
probright_dbControlCold <- exp(deli_blue$b_cortControl + deli_blue$b_Intercept)/(1+exp(deli_blue$b_cortControl + deli_blue$b_Intercept))
probright_dbCORTHot <- exp(deli_blue$b_tempHot + deli_blue$b_Intercept)/(1+exp(deli_blue$b_tempHot + deli_blue$b_Intercept))
probright_dbControlHot <- exp(deli_blue$'b_cortControl:tempHot' + deli_blue$b_cortControl + deli_blue$b_tempHot + deli_blue$b_Intercept)/(1+exp(deli_blue$'b_cortControl:tempHot' + deli_blue$b_cortControl + deli_blue$b_tempHot + deli_blue$b_Intercept))

@@

probright_grCORTCold <- exp(guich_red$b_Intercept)/(1+exp(guich_red$b_Intercept))
probright_grControlCold <- exp(guich_red$b_cortControl + guich_red$b_Intercept)/(1+exp(guich_red$b_cortControl + guich_red$b_Intercept))
probright_grCORTHot <- exp(guich_red$b_tempHot + guich_red$b_Intercept)/(1+exp(guich_red$b_tempHot + guich_red$b_Intercept))
probright_grControlHot <- exp(guich_red$'b_cortControl:tempHot' + guich_red$b_cortControl + guich_red$b_tempHot + guich_red$b_Intercept)/(1+exp(guich_red$'b_cortControl:tempHot' + guich_red$b_cortControl + guich_red$b_tempHot + guich_red$b_Intercept))

@@

probright_gbCORTCold <- exp(guich_blue$b_Intercept)/(1+exp(guich_blue$b_Intercept))
probright_gbControlCold <- exp(guich_blue$b_cortControl + guich_blue$b_Intercept)/(1+exp(guich_blue$b_cortControl + guich_blue$b_Intercept))
probright_gbCORTHot <- exp(guich_blue$b_tempHot + guich_blue$b_Intercept)/(1+exp(guich_blue$b_tempHot + guich_blue$b_Intercept))
probright_gbControlHot <- exp(guich_blue$'b_cortControl:tempHot' + guich_blue$b_cortControl + guich_blue$b_tempHot + guich_blue$b_Intercept)/(1+exp(guich_blue$'b_cortControl:tempHot' + guich_blue$b_cortControl + guich_blue$b_tempHot + guich_blue$b_Intercept))

@@

Model formula for task is:  
Choice  ~ Trial*cort*temp + (1 + Trial|lizard_id)  
Plots for the different models of the associative task:  
1.- _L. delicata_  
  1.a.- Red  
```{r , plotmod_dar, out.width="70%", fig.align="center"}
plot(mod_dar)
bayes_R2(mod_dar)
```
```{r, results='asis', echo=FALSE}
cat("\\newpage")
```
